\cvsection{Job Experience}
\begin{cventries}
    \cventry
    {Engineering Manager}
    {Scotiabank Colpatria}
    {Bogotá, Colombia}
    {February 2023 - Present}
    {
        \begin{cvitems}
            \item {Leader of technical teams responsible for authentication and fraud-related initiatives.}
            \item {Responsible for the design, coding, testing, and release process of requirements and enhancements for personal banking web and mobile applications.}
        \end{cvitems}
    }

    \cventry
    {Software Development Project Leader}
    {Mercado Libre}
    {Bogotá, Colombia}
    {July 2021 - January 2023}
    {
        \begin{cvitems}
            \item {Project leader in the banking connections business unit, overseeing the development process and career progression of the team's developers.}
            \item {Leader of the B2B vertical, responsible for modeling and implementing fintech software in Argentina and Brazil. (July 2021 - December 2021)}
            \item {Leader of the "Banking Connection - Mercado Pago Argentina" vertical, overseeing the implementation of payment mechanisms and regulations in Argentina. (January 2022 - Present)}
        \end{cvitems}
    }

    \cventry
    {Junior Software Architect}
    {Aval Digital Labs}
    {Bogotá, Colombia}
    {July 2019 - June 2021}
    {
        \begin{cvitems}
            \item {Software architect for the "Distribución digital de Fondos de Inversión Colectiva" (Digital Distribution of Mutual Funds) project, a financial product of Fiduciaria Bogotá.}
            \item {Technical team leader responsible for aligning business vision with technology.}
        \end{cvitems}
    }

    \cventry
    {Backend Development Analyst}
    {}
    {Bogotá, Colombia}
    {December 2018 - June 2019}
    {
        \begin{cvitems}
            \item {Backend Developer for Personal Banking at AV Villas Bank.}
            \item {Supported software architecture decisions as a member of the internal Architecture chapter.}
        \end{cvitems}
    }

    \cventry
    {Senior Backend Developer}
    {Almundo}
    {Bogotá, Colombia}
    {June 2018 - November 2018}
    {
        \begin{cvitems}
            \item {Member of the "Growth IT" team, responsible for creating customer journeys based on recommendation systems.}
        \end{cvitems}
    }

    \cventry
    {Backend Developer}
    {Rappi S.A.S}
    {Bogotá, Colombia}
    {June 2017 - May 2018}
    {
        \begin{cvitems}
            \item {Supported Rappi S.A.S.'s core backend platform.}
            \item {Technical leader for the third-party integrations department.}
        \end{cvitems}
    }

    \cventry
    {Backend Developer / Data Scientist}
    {Cloud RT Analytics}
    {Zulia, Venezuela}
    {March 2016 - June 2017}
    {
        \begin{cvitems}
            \item {Developed predictive models for Data Science activities.}
            \item {Developed the AGA Core TM architecture.}
        \end{cvitems}
    }

    \cventry
    {Java Backend Developer / Linux Server Administrator}
    {Insignia Mobile Communications}
    {Zulia, Venezuela}
    {September 2013 - February 2016}
    {
        \begin{cvitems}
            \item {Support engineer for a custom SMS software platform based on the SMPP protocol and TX/RX/TRX architecture.}
            \item {Lead engineer for server migration and security operations.}
            \item {Provided outsourcing and consulting services for third-party clients in Web and SMS solutions.}
        \end{cvitems}
    }

    \cventry
    {Internship}
    {Centro de Modelado Científico - CMC}
    {Zulia, Venezuela}
    {June 2013 – November 2013}
    {
        \begin{cvitems}
            \item {Intern in the Department of Astronomy and Theoretical Physics.}
            \item {Developed a tool for visualizing and analyzing the spectral information of celestial bodies.}
        \end{cvitems}
    }
\end{cventries}
